%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

% TODO: use a for loop here or something
\newcommand{\resumeSubheadingWithPromotion}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/abdulrahman-alhamali-b9578378/}{\Large Abdulrahman Alhamali}} & Email : \href{mailto:a.alhamali93@gmail.com}{a.alhamali93@gmail.com}\\
  \href{https://www.linkedin.com/in/abdulrahman-alhamali-b9578378/}{https://www.linkedin.com/in/abdulrahman-alhamali-b9578378/} & Mobile : +1-514-550-54-84 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {American University of Beirut}{Beirut, Lebanon}
      {Bachelor of Computer and Communications Engineering;  GPA: 89.06\%}{Feb. 2012 -- Jan. 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Development Experience}
  \resumeSubHeadingListStart
    \resumeSubheadingWithPromotion
      {Shopify}{Toronto, Ontario}
      {Staff Site Reliability Engineer - Resiliency}{April 2024 - Present}
      {Senior Site Reliability Engineer - Resiliency}{March 2022 - April 2024}
      \resumeItemListStart
      \resumeItem{Technical Leadership}
          {Leading several of our team's engagements and projects. Disambiguating the needs, defining the technical approach, scoping the work, and leading a "squad" within our team to get the work done.}
      \resumeItem{Operational Leadership}
          {Took charge during the critical phase of a migration of our deploy system, leading on-the-ground operations, developing operational manuals, streamlining communications, and collaborating with tooling teams and leadership.}
      \resumeItem{Scale Testing} 
          {Took leadership of BFCM scale testing during 2023, which involved planning, coordinating, leading, and retrospecting on 5 large-scale tests that caught several insidious issues and helped us achieve a smooth BFCM. }
        \resumeItem{Incident Management}
          {Managing a wide range of incidents throughout their lifecycle from detection into mitigation, resolution and retrospection, and introducing several improvements to the process. }
	\resumeItem{Developing Systemic Approaches to Resiliency}
          {Introduced a mental framework "Resiliency Risk Repository" to help service designers understand different resiliency risks and navigate them, and leading the effort to promote this framework and develop it.}
	\resumeItem{Introducing Novel Resiliency Measures}
	  {Introduced and implemented Envoy's Adaptive Concurrency as a form of load shedding. This included designing our approach, rigorously testing it, and rolling it out incrementally.}
        \resumeItem{Service Ownership} 
          {Took ownership of a service responsible for bot defense, led the effort to scale it to process upwards of 80 Million RPM, introduced actionable SLOs, and introduced the team to a data-driven approach for evolving it. }
	\resumeItem{Training and Mentorship}
	  {Mentoring interns and junior members and providing personalized 1-1 troubleshooting, shadowing, and pairing sessions. In addition to identifying gaps in our training and devising novel team-wide training sessions to address them.}
      \resumeItemListEnd

    \resumeSubheading
      {AppDirect}{Montréal, Québec}
      {Senior Technical Operations Developer - Observability}{March 2021 - March 2022}
      \resumeItemListStart
        \resumeItem{RBIS}
          {Initiated and implemented a change-tracking project (using GoLang, Kafka, and BigQuery) to enable users in case of incident to quickly review change events generated from different areas and pinpoint possible causes.  }
        \resumeItem{Datadog Integrations}
          {Implemented tools (in Golang) to enable users to effectively leverage different features of Datadog, such as tracing, synthetic checks, and monitors}
        \resumeItem{Load Balancer Refactoring}
          {Researched and executed a refactoring of our load balancers that streamlines the provisioning of new LBs using Terraform, and limits their accessibility to only through the WAF}
        \resumeItem{Kubernetes upgrades, migrations, and troubleshooting} 
          {Executed several EKS/AKS upgrades, and instructed operators on doing that, participated in kOps/EKS migrations, and led the troubleshooting effort for a CPU spike issue in AKS }
      \resumeItemListEnd

    \resumeSubheading
      {Coveo}{Montréal, Québec}
      {DevOps Tooling Software Engineer}{Jan 2019 - March 2021}
      \resumeItemListStart
        \resumeItem{Spinnaker Migration}
          {Initiated and implemented a project to migrate development teams from a centralized Jenkins-based deployment pipeline to a per-team Spinnaker-based pipeline with minimum interruption. In executing the project, I had to contribute significant changes to Open Source Spinnaker to make it fit our needs. }
        \resumeItem{Automated Deployment Monitoring}
          {Initiated, researched and implemented a system to automatically monitor health metrics of micro-services while deploying, and rollback automatically if any degradation was noticed}
        \resumeItem{Config Migration Script}
          {Moved our deployment pipeline from version-based to evergreen by implementing a workflow that included standardized deprecation and automated migration procedures}
        \resumeItem{Miscellaneous} 
          {Creating internal documentation, providing support for users, collecting requirements, supervising interns, and organizing a recurring "DevOps Meetup" conference}
      \resumeItemListEnd
      
% % --------Multiple Positions Heading------------
% %    \resumeSubSubheading
% %     {Software Engineer I}{Oct 2014 - Sep 2016}
% %     \resumeItemListStart
% %        \resumeItem{Apache Beam}
% %          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
% %     \resumeItemListEnd
% %    \resumeSubHeadingListEnd
% %-------------------------------------------

    \resumeSubheading
      {SAUGO360}{Beirut, Lebanon}
      {Software Engineer}{Jan 2016 - Jan 2019}
      \resumeItemListStart
        \resumeItem{SAUGO360 Golden Config Manager}
          {Worked on a web portal in Angular and NestJS for SAUGO360 GCM, a platform built on top of NSO (Network Services Orchestrator).}
        \resumeItem{SAUGO360 OpenDaylight Controller}
          {Worked on an Angular-based web portal for SAUGO360 ODL Controller, a collection of networking features built on top of OpenDaylight.}
        \resumeItem{Momday}
          {Worked on a Flutter-based Mobile app for the e-commerce platform Momday.}
        \resumeItem{Miscellaneous}
          {Supervised multiple internship programs, studied feasability and requirments of several projects, and worked on the CI/CD of the products.}
      \resumeItemListEnd

    \resumeSubheading
      {OpenDayLight TSDR Project}{Remote Volunteering}
      {Testing Engineer}{Jun 2016 - May 2018}
      \resumeItemListStart
        \resumeItem{Automated Tests}
          {Developed and maintained automated tests for the TSDR Project using Robot Framework and Jenkins.}
        \resumeItem{TSDR RESTCONF Collector}
          {Developed a collector that collects RESTCONF requests received by ODL and persists them in the TSDR database.}
      \resumeItemListEnd

    \resumeSubheading
      {Dar Al-Handasah}{Beirut, Lebanon}
      {Freelance Software Developer}{Summer 2015}
      \resumeItemListStart
        \resumeItem{Urban Street Design Tool (USDM)}
          {Used Java and GWT to design and implement a geometric algorithm that calculates intersections between circles, and implemented user-behavior tracking using Google Analytics.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Other Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {American University of Beirurt}{Beirut, Lebanon}
      {Research Assistant - Lab Assistant - Freelance Tutor}{Feb 2012 - Jan 2016}
    
    \resumeSubheading
      {ToastMasters Lebanon}{Beirut, Lebanon}
      {Convention Chair - Secretary - Club Vice President} {2013 - 2015}
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/AbdulRahmanAlHamali/flutter_typeahead}{Flutter Typeahead}}
      {Open source Flutter widget to show users suggestions as they type.}
    \resumeSubItem{\href{https://github.com/AbdulRahmanAlHamali/flutter_pagewise}{Flutter Pagewise}}
      {Open source Flutter widget that loads its content one page at a time.}
  \resumeSubHeadingListEnd


 %--------LANGUAGES------------
\section{Lanugages}
  \begin{tabular*}{\textwidth}{c@{\extracolsep{\fill}}ll}
    \textbf{Arabic:} Native & \textbf{English:} Fluent & \textbf{French:} Working Proficiency\\
  \end{tabular*}

\lfoot{C.V. format was adopted from the \href{https://github.com/sb2nov/resume}{Open Source LaTeX template} by Sourabh Bajaj}
%-------------------------------------------
\end{document}
